Paper Title*\\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used} \thanks{Identify applicable funding agency here. If none, delete this.}

### 2019-05-01 icdm/submission/includes/evaluation.tex
table and figure form

\begin{table}[tb]
\caption{Example of a sentence with different sampling tresholds}
    %\scriptsize
    \begin{tabular}{l l}%
        \toprule
Sampling Treshhold & 0 \\

        \midrule%
Sampling Treshold & First sentence of Dataset \\ \hline
$10^{-1}$ &Anarchism originated as a term of abuse first\tabularnewline used against early working class radicals \tabularnewline including the diggers of the english \\ \hline
$10^{-2}$ & Anarchism originated as a term of abuse first used against early \tabularnewline working class radicals including diggers of english \\ \hline
$10^{-3}$ & Anarchism originated a term abuse first used against early \tabularnewline working class radicals including diggers the english\\ \hline
$10^{-4}$ & Anarchism originated abuse used against working class radicals\tabularnewline diggers english \\ \hline
$10^{-5}$ & against radicals diggers \\ \hline        
        \midrule%
   \end{tabular}%
\label{table:treshold_examples}
\end{table}

@@

\begin{table}[]
\centering
\begin{tabular}{|l|l|l|}
\hline
Word1 & Word2 & Score \\ \hline
\textquote{FBI} & \textquote{Investigation} & \textquote{8.31} \\ \hline
\textquote{Mars} & \textquote{scientist} & \textquote{5.63} \\ \hline
\end{tabular}
\caption{Example of pairs and their rating in wordsim353}
\label{fig:ws353_ex}
\end{table}

>>>>

\begin{table*}[tb]\centering
\caption{Example of a sentence with different sampling tresholds}
    %\scriptsize
    \begin{tabular}{l l}%
        \toprule
Sampling Treshold & First sentence of Dataset \\ 
        \midrule%
$10^{-1}$ & \makecell[l]{Anarchism originated as a term of abuse first used against early working class radicals including the diggers\\ of the english} \\ \hline
$10^{-2}$  & \makecell[l]{ Anarchism originated as a term of abuse first used against early \\ working class radicals including diggers of english} \\ \hline
$10^{-3}$ & \makecell[l]{Anarchism originated a term abuse first used against early \\ working class radicals including diggers the english}\\ \hline
$10^{-4}$ &\makecell[l]{ Anarchism originated abuse used against working class radicals\\ diggers english} \\ \hline
$10^{-5}$ & against radicals diggers \\ \hline        
        \midrule%
   \end{tabular}%
\label{table:treshold_examples}
\end{table*}

@@

\begin{table}[tb]\centering
\caption{Example of pairs and their rating in wordsim353}
\begin{tabular}{l l l }
        \toprule
Word1 & Word2 & Score \\ \hline
        \midrule%

\textquote{FBI} & \textquote{Investigation} & 8.31 \\ \hline
\textquote{Mars} & \textquote{scientist} & 5.63 \\ \hline
        \midrule%
\end{tabular}
\label{fig:ws353_ex}
\end{table}
